---
title: "Challenge-6"
author: "shuohang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

```{r, out.height= "20px",out.width= "200px",echo=FALSE}
```

```{r, out.height= "20px",out.width= "200px",echo=FALSE}
```

**Solutions:**

```{r, eval=T,echo=TRUE}
# Enter code here

library(systemfonts)
print_countdown <- function(num) {
  cat(num, "\n")
}
countdown <- 10
while (countdown >= 1) {
  print_countdown(countdown)
  Sys.sleep(1)
  countdown <- countdown - 1
}
cat("Blastoff!\n")


```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Enter code here
reverse_string <- function(input_string) {
  reversed <- ""
  for (i in nchar(input_string):1) {
    reversed <- paste(reversed, substr(input_string, i, i), sep = "")
  }
  return(reversed)
}
#word <- readline(prompt = "Enter a word: ")

reversed_word <- reverse_string("hello")
cat("Reversed word: ", reversed_word, "\n")



```
<br>
