---
title: "Challenge-2"
author: "xiaoshuohang"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{=html}
<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>
```
<br> <br>

::: {.alert .alert-info}
<strong>Welcome!</strong> Hope you have watched the lecture videos and
followed the instructions in code-along. Go through the steps described
below, *carefully*. It is totally fine to get stuck - <strong>ASK FOR
HELP</strong>; reach out to your friends, TAs, or the discussion forum
on Canvas.

 

Here is what you have to do, <br> <br>

1.  <strong>Pair</strong> with a neighbor and work

2.  <strong>Download</strong> the `Challenge-2.Rmd` and
    `playlist_data.csv` files from Canvas

3.  <strong>Move</strong> the downloaded files to the folder, "Week-2"

4.  <strong>Set</strong> it as the working directory

5.  <strong>Edit</strong> content wherever indicated

6.  <strong>Remember</strong> to set `eval=TRUE` after completing the
    code to generate the output

7.  <strong>Ensure</strong> that `echo=TRUE` so that the code is
    rendered in the final document

8.  <strong>Inform</strong> the tutor/instructor upon completion

9.  <strong>Submit</strong> the document on Canvas after they approve

10. <strong>Attendance</strong> will be marked only after submission

11. Once again, <strong>do not hesitate</strong> to reach out to the
    tutors/instructor, if you are stuck
:::

<br>

# I. Exploring music preferences

### A. Background

Imagine that you have been hired as a data analyst by a radio station to
analyze music preferences of their DJs. They have provided you with a
dataset, `playlist_data.csv`, containing information about DJs, their
preferred music genres, song titles, and ratings.

Using the data-set you are required to complete some tasks that are
listed subsequently. All these tasks are based on the concepts taught in
the video lectures. The questions may not be entirely covered in the
lectures; To complete them, you are encouraged to use Google and the
resources therein. <br>

### B.Tasks

#### Task-1

In the lecture, we used two data-sets, `starwars` and
`anscombe's quartet` that were readily available with the packages,
`tidyverse` and `Tmisc`, respectively. When we have to use custom-made
data-sets or the ones like we downloaded from Canvas, we have to import
it using the R commands before using them. All the questions below are
related to this task. <br> <br>

**Question 1.1:** What does the term "CSV" in `playlist_data.csv` stand
for, and why is it a popular format for storing tabular data?

**Solution:** it stand for comma seperated values,it is popular for its
simplicity and compatibility. <br> <br> **Question 1.2:** load the
`tidyverse` package to work with `.csv` files in R.

**Solution:**

```{r,echo=TRUE,eval=TRUE}
# Load the necessary package to work with CSV files in R.
library(tidyverse)
```

<br>

**Question 1.3:** Import the data-set, `playlist_data.csv`

**Solution:** read_csv("playlist_data.csv")

```{r,echo=TRUE,eval=TRUE}
read_csv("playlist_data.csv")
```

<br>

**Question 1.4:** Assign the data-set to a variable, `playlist_data`

**Solution:** x <- read_csv("playlist_data (2).csv")

```{r,echo=TRUE,eval=FALSE}
# Assign the variable to a dataset 

insert_name_of_variable <- read_csv("insert_name_of_dataset_with_extension") 

```

*From now on, you can use the name of the variable to view the contents
of the data-set* <br> <br>

**Question 1.5:** Get more information about `read_csv()` command and
provide a screenshot of the information displayed in the "Help" tab of
the "Files" pane

**Solution:**

```{r,echo=TRUE,eval=FALSE}
# More information about the R command, complete the code

read_csv()

```

<br>

```{r, out.height= "400px",out.width= "800px",echo=TRUE,eval=FALSE,fig.cap="Insert caption here"}
knitr::include_graphics("name_of_the_file_with_extension")
```

<br>

**Question 1.6:** What does the `skip` argument in the read_csv()
function do?

**Solution:** *The skip argument in the read_csv() function (from the readr package in R) is used to specify the number of lines that should be skipped while reading a CSV file. * <br> <br>

**Question 1.7:** Display the contents of the data-set

**Solution:** View(X)

```{r,echo=TRUE,eval=FALSE}
# Type the name of the variable, to see what it contains


```

<br>

**Question 1.8:** Assume you have a CSV file named `sales_data.csv`
containing information about sales transactions. How would you use the
`read_csv()` function to import this file into R and store it in a
variable named `sales_data`?

**Solution:*read_csv("sales_data.csv") ,`sales_data`<- read_csv("sales_data.csv") *

```{r,echo=TRUE,eval=FALSE}
# No output is required for this code
# Only the list of commands that execute the task mentioned in the question are required

```

<br> <br>

#### Task-2

After learning to import a data-set, let us explore the contents of the
data-set through the following questions <br> <br>

**Question 2.1:** Display the first few rows of the data-set to get an
overview of its structure

**Solution:**

```{r,echo=TRUE,eval=FALSE}
# Type the name of the variable we assigned the data-set to
head(name_of_the_variable)
> head(X)
```

<br>

**Question 2.2:** Display all the columns of the variable stacked one
below another

**Solution:**

```{r,echo=TRUE,eval=FALSE}
# Stack columns of playlist_data

```

<br>

**Question 2.3:** How many columns are there in the dataset?

**Solution:**ncol(X),7

```{r,echo=TRUE,eval=FALSE}
# Number of columns
```

<br>

**Question 2.4:** What is the total count of DJs?

**Solution:**X$DJ_Name 26  [1] "DJ A" "DJ B" "DJ C" "DJ D" "DJ E" "DJ F" "DJ G" "DJ H" "DJ I" "DJ J" "DJ K" "DJ L" "DJ M"
[14] "DJ N" "DJ O" "DJ P" "DJ Q" "DJ R" "DJ S" "DJ T" "DJ U" "DJ V" "DJ W" "DJ X" "DJ Y" "DJ Z"

```{r,echo=TRUE,eval=FALSE}
# Number of DJs
```

<br>

**Question 2.5:** Display all the location of all the DJs

**Solution:**X$Location
[1] "City X" "City Y" "City Z" "City X" "City Y" "City Z" "City X" "City Y" "City Z" "City X"
[11] "City Y" "City Z" "City X" "City Y" "City Z" "City X" "City Y" "City Z" "City X" "City Y"
[21] "City Z" "City X" "City Y" "City Z" "City X" "City Y"

```{r,echo=TRUE,eval=FALSE}
# Location of DJs
```

<br>

**Question 2.6:** Display the age of the DJs

**Solution:**X$Age [1] 28 24 30 22 27 25 29 23 31 26 32 28 29 25 31 26 27 24 29 23 28 24 30 22 27 25

```{r,echo=TRUE,eval=FALSE}
# Age of DJs
```

<br> <br>

#### Task-3

Let us plot the data to get more insights about the DJs. <br> <br>

**Question 3.1:** Create a plot to visualize the relationship between
DJs' ages and their ratings.

**Solution:**
ggplot(X) +aes(x=Age,y=Rating)
```{r,echo=TRUE,eval=FALSE}
# complete the code to generate the plot

ggplot(name_of_the_variable) 

aes(x=column_name,y=column_name)

```

<br>

**Question 3.2:** Label the x-axis as "Age" and the y-axis as "Rating."

**Solution:**

```{r,echo=TRUE,eval=FALSE}
# complete the code to generate the plot

ggplot(name_of_the_variable) 

aes(x=column_name,y=column_name)

```

<br>

**Question 3.3:** Represent data using points

**Solution:**ggplot(X) +aes(x=Age,y=Rating)+geom_point()

```{r,echo=TRUE,eval=FALSE}
# complete the code to generate the plot

ggplot(name_of_the_variable) 

aes(x=column_name,y=column_name)

```

<br>

**Question 3.4:** Can you change the points represented by dots/small
circles to any other shape of your liking?

**Solution:**

```{r,echo=TRUE,eval=FALSE}
# complete the code to generate the plot

ggplot(name_of_the_variable) 

aes(x=column_name,y=column_name)

 # <-- Hint: Use ? to learn more about geom_point and use appropriate values for shape

```

<br>

**Question 3.5:** Insert a suitable title and briefly provide your
insights in the caption

**Solution:**ggplot(X) +aes(x=Age,y=Rating)+geom_point()+labs(title="age versus ratings",caption="Source:playlist_data")

```{r,echo=TRUE,eval=FALSE}
# complete the code to generate the plot

ggplot(name_of_the_variable) 

aes(x=column_name,y=column_name)

```

<br>
