---
pdf_document: default
author: "xiaoshuohang"
date: "`r Sys.Date()`"
output:
  html_document: null
  df_print: paged
  pdf_document: default
title: "Week-3: Code-along"
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# I. Code to edit and execute

**To be submitted on canvas before attending the tutorial**


### Loading packages

```{r, eval=FALSE,echo=TRUE}
# Load package tidyverse

```

### Assigning values to variables

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Example a.: execute this example
x <- 'A'
x
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example b and execute it
x <-"Apple"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example c and execute it
x<-FALSE
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example d and execute it
 x <- 5L
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example e and execute it
x <- 5
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example f and execute it
 x <-1i
```

### Checking the type of variables

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Example a.: execute this example
x <- 'A'
typeof(x)
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example b and execute it
[1] "character"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example c and execute it
[1] "logical"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example d and execute it
[1] "integer"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example e and execute it
[1] "double"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Complete the code for Example f and execute it
"complex"c
```

### Need for data types

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# import the cat-lovers data from the csv file you downloaded from canvas
cat_lovers<- read_csv("cat-lovers.csv")
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Compute the mean of the number of cats: execute this command
mean(cat_lovers$number_of_cats)
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Get more information about the mean() command using ? operator
?mean
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Convert the variable number_of_cats using as.integer()
mean(as.integer(cat_lovers$number_of_cats))
[1] NA
Warning message:
In mean(as.integer(cat_lovers$number_of_cats)) : NAs introduced by coercion
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Display the elements of the column number_of_cats 
 cat_lovers$number_of_cats
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Display the elements of the column number_of_cats after converting it using as.numeric()
as.integer(cat_lovers$number_of_cats)
 [1]  0  0  1  3  3  2  1  1  0  0  0  0  1  3  3  2  1  1  0  0  1  1  0  0  4  0  0  0  0  0  0
[32]  0  0  0  0  0  0  0  0  0  0  0  1  3  3  2  1 NA  0  0  1  0  1 NA  1  1  1  0  0  2
Warning message:
NAs introduced by coercion 
```

### Create an empty vector

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Empty vector
x<-vector()
# Type of the empty vector
typeof(x)
[1] "logical"
```

### Create vectors of type logical

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 1
x<-vector("logical",length=5)
# Display the contents of x
print(x)
# Display the type of x
print(typeof(x))
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 2
x<-logical(5)
# Display the contents of x
print(x)
# Display the type of x
print(typeof(x))
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 3
x<-c(TRUE,FALSE,TRUE,FALSE,TRUE)
# Display the contents of x
print(x)
# Display the type of x
print(typeof(x))
```

### Create vectors of type character

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 1
 x<-vector("character",length=5)
# Display the contents of x

# Display the type of x
typeof(x)
[1] "character"
print(typeof(x))
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 2
x<-character(5)
# Display the contents of x
print(x)
# Display the type of x
[1] "character"
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 3
x<-c('A','b','r','q')
# Display the contents of x

# Display the type of x
[1] "character"
```

### Create vectors of type integer

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 1
 x<-vector("integer",length=5)
# Display the contents of x

# Display the type of x
print(typeof(x))
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 2
x<-integer(5)
# Display the contents of x
print(x)
# Display the type of x

```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 3
 X<-c(1,2,3,4,5)
# Display the contents of x

# Display the type of x
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 4
x<-seq(from=1,to=5,by=0.1)
# Display the contents of x

# Display the type of x
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 5
x<-1:5
# Display the contents of x

# Display the type of x
```

### Create vectors of type double

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 1
 x<-vector("double",length=5)
# Display the contents of x

# Display the type of x
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 2
x<-double(5)
# Display the contents of x

# Display the type of x
```

```{r,warning=TRUE,message=FALSE,eval=FALSE,echo=TRUE}
# Method 3
x<-c(1.5,2.0,2.5)
# Display the contents of x

# Display the type of x
```

### Implicit coercion

#### Example 1

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector
x<-vector()
# Check the type of x
"logical"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Add a character to the vector
x<-c(1.8)
# Check the type of x
"double"
```

#### Example 2

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector

# Check the type of x

```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Add a number to the vector
 x<-c(x,'a')
# Check the type of x
"character"
```

#### Example 3

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector

# Check the type of x

```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Add a logical value to the vector
x<-c(x,TRUE)
# Check the type of x
"character"
```


#### Example 4

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector
 x<-c(1L)
# Check the type of x
 "integer"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Add a number to the vector
x<-c(x,2)
# Check the type of x
[1] "double"
```

### Explicit coercion

#### Example 1

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector
x<-c(1L)
# Check the type of x
"integer"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Convert the vector to type character
 x<-as.character(x)
# Check the type of x
"character"
```

#### Example 2

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector
x<-c('A')
# Check the type of x
character
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Convert the vector to type double
 x<-as.numeric(x)
# Check the type of x
"double"
```

### Accessing elements of the vector

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Create a vector
x <- c(1,10,9,8,1,3,5)
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Access one element with index 3
x[3]
[1] 9
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Access elements with consecutive indices, 2 to 4: 2,3,4
x[2:4]
[1] 10  9  8
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Access elements with non-consecutive indices, 1,3,5
 x[c(1,3,5)]
[1] 1 9 1
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Access elements using logical vector
x[c(TRUE,FALSE,FALSE,TRUE,FALSE,FALSE,TRUE)]
[1] 1 8 5
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Access elements using the conditional operator <
x[x<9]
[1] 1 8 1 3 5
```

### Examining vectors

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Display the length of the vector
print(length(x))
# Display the type of the vector
print(typeof(x))
# Display the structure of the vector
print(str(x))
```

### Lists

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Initialise a named list
my_pie = list(type="key lime", diameter=7, is.vegetarian=TRUE)
# display the list
my_pie
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Print the names of the list
[1] "type"          "diameter"      "is.vegetarian"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Retrieve the element named type
[1] "key lime"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Retrieve a truncated list
$type
[1] "key lime"
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Retrieve the element named type
[1] "key lime"
```

#### Exploring data-sets

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Install package
install.packages("openintro")
# Load the package
library(openintro)
# Load package
library(tidyverse)
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Catch a glimpse of the data-set: see how the rows are stacked one below another
glimpse(loans_full_schema)
```


```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Selecting numeric variables
loans <- loans_full_schema %>% # <-- pipe operator
  select(paid_total, term, interest_rate,
         annual_income,paid_late_fees,debt_to_income)
# View the columns stacked one below another
glimpse(loans)
Rows: 10,000
Columns: 6
$ paid_total     <dbl> 1999.330, 499.120, 281.800, 3312.890, 2324.650, 873.130, 2730.510, 1765.84…
$ term           <dbl> 60, 36, 36, 36, 36, 36, 60, 60, 36, 36, 60, 60, 36, 60, 36, 60, 60, 60, 36…
$ interest_rate  <dbl> 14.07, 12.61, 17.09, 6.72, 14.07, 6.72, 13.59, 11.99, 13.59, 6.71, 15.04, …
$ annual_income  <dbl> 90000, 40000, 40000, 30000, 35000, 34000, 35000, 110000, 65000, 30000, 750…
$ paid_late_fees <dbl> 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,…
$ debt_to_income <dbl> 18.01, 5.04, 21.15, 10.16, 57.96, 6.46, 23.66, 16.19, 36.48, 18.91, 10.45,…
> 
```

```{r,warning=TRUE,message=TRUE,eval=FALSE,echo=TRUE}
# Selecting categoric variables
loans <- loans_full_schema %>% 
  select( ) # type the chosen columns as in the lecture slide
# View the columns stacked one below another
glimpse(loans)
Rows: 10,000
Columns: 4
$ grade               <fct> C, C, D, A, C, A, C, B, C, A, C, B, C, B, D, D, D, F, E, C, A, B, C, …
$ state               <fct> NJ, HI, WI, PA, CA, KY, MI, AZ, NV, IL, IL, FL, SC, CO, FL, TN, NV, N…
$ homeownership       <fct> MORTGAGE, RENT, RENT, RENT, RENT, OWN, MORTGAGE, MORTGAGE, MORTGAGE, …
$ disbursement_method <fct> Cash, Cash, Cash, Cash, Cash, Cash, Cash, Cash, Cash, Cash, Cash, Cas…
> 
```