---
title: "Challenge-5"
author: "shuohang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
x<-5
function1<-function(x=10){x+0}
function1(x=10)
function1(x)
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
total<-5
function2<-function(x){total+x}
function2(x=1)
function2(x=2)
function2(x=3)
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
total<-100
function3.2<-function(x){x+total}
function3.2(1)
function3.2(2)
```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
inner_function<-function(x){print(x)}
outer_function<-function(x,inner_function){x<-5 
inner_function<-print(x)}

outer_function(x)
inner_function(x)


```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
#install.packages("magick")
library(magick)
creat_meme<-function(text,image_path,output_path){
  meme<-image_read(image_path)
  meme<-image_annotate(meme,text,gravity="center",size=50,color="black")
  image_write(meme,path=output_path)}
creat_meme("hi","1.png","output_meme.jpg")

```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
text_analysis_game <- function() {
  cat("Welcome to the Text Analysis Game!\n")
  user_input <- readline(prompt = "Enter a sentence: ")
  words <- strsplit(user_input, " ")
  num_words <- length(words)
  num_chars <- nchar(user_input)
}
text_analysis_game()
```
<br>